How to control for non-independence in cross-national analyses: An R tutorial

### 2022-11-21 vignette.Rmd
update vignette

```{r echo=F}
options(width = 300)
```

@@

```{r echo=FALSE}
# load data from targets cache
spatialSimData <- tar_read(simData_simGeoCov_0.8_0.8_1728b220)
# only OECD countries for example, country iso codes
oecd <- c("AT","AU","BE","CA","CH","CL","CZ","DE","DK",
          "EE","ES","FI","FR","GB","GR","HU","IE","IL",
          "IS","IT","JP","KR","LT","LU","LV","MX","NL",
          "NO","NZ","PL","PT","SE","SI","SK","TR","US")
spatialSimData <- filter(spatialSimData, country %in% oecd)
# write data to file
write.csv(file = "data/vignette/spatialSimData.csv", 
          spatialSimData, row.names = FALSE)
```

@@

```{r echo=FALSE}
# load data from targets cache
culturalSimData <- tar_read(simData_simLinCov_0.8_0.8_0fb442ad)
# only OECD countries
culturalSimData <- filter(culturalSimData, country %in% oecd)
# write data to file
write.csv(file = "data/vignette/culturalSimData.csv", 
          culturalSimData, row.names = FALSE)
```

>>>>

```{r echo=F}
options(width = 300)
oecd <- c("AT","AU","BE","CA","CH","CL","CZ","DE","DK",
          "EE","ES","FI","FR","GB","GR","HU","IE","IL",
          "IS","IT","JP","KR","LT","LU","LV","MX","NL",
          "NO","NZ","PL","PT","SE","SI","SK","TR","US")
```

@@

@@
